\RequirePackage{pdfmanagement}
\documentclass[a4paper]{l3doc}

\makeatletter
\disable@package@load{parskip}{}
\makeatother

\input{biblatex-sbl-examples-preamble.tex}

\setcounter{tocdepth}{2}
\setcounter{secnumdepth}{3}

% SBL style footnotes
\usepackage[bottom, ragged]{footmisc}
\makeatletter
\renewcommand*{\@makefntext}[1]{%
  \parindent \footnotemargin
  \@thefnmark . \enspace
  \footnotelayout #1}
\renewcommand{\thempfootnote}{\arabic{mpfootnote}}

% redefine \maketitle to better match \thanks footnote
\renewcommand\maketitle{\par
  \begingroup
    \renewcommand\thefootnote{\@fnsymbol\c@footnote}%
    \renewcommand*{\@makefntext}[1]{%
      \parindent \footnotemargin
      \@textsuperscript{\@thefnmark}%
      \footnotelayout ##1}%
    \if@twocolumn
      \ifnum \col@number=\@ne
        \@maketitle
      \else
        \twocolumn[\@maketitle]%
      \fi
    \else
    \newpage
      \global\@topnum\z@   % Prevents figures from going at top of page.
      \@maketitle
    \fi
    \thispagestyle{plain}\@thanks
  \endgroup
  \setcounter{footnote}{0}%
  \global\let\thanks\relax
  \global\let\maketitle\relax
  \global\let\@maketitle\relax
  \global\let\@thanks\@empty
  \global\let\@author\@empty
  \global\let\@date\@empty
  \global\let\@title\@empty
  \global\let\title\relax
  \global\let\author\relax
  \global\let\date\relax
  \global\let\and\relax
}
\makeatother

\usepackage[skins]{tcolorbox}
\newtcolorbox{sblexample}[1][]{%
  bicolor, colframe=black, colback=black!15, colbacklower=white, left=2mm,
  fonttitle=\normalsize\sffamily\bfseries,
  subtitle style={before skip=3mm, after skip=3mm},
  right=2mm, sidebyside, sidebyside gap=6mm, sidebyside align=top, lefthand
  ratio=0.5, before skip=\bigskipamount, after skip=\bigskipamount, before
  lower=\newrefsection\parindent 0pt\parskip\medskipamount\begin{NoHyper},
  after lower=\end{NoHyper}\endrefsection, #1
}
\tcbset{%
  no output/.style={standard, sidebyside=false},
  no code/.style={standard, colback=white, sidebyside=false, before
    upper=\newrefsection\parindent 0pt\parskip\medskipamount\begin{NoHyper},
  after upper=\end{NoHyper}\endrefsection}
}

\begin{document}

\title{The \pkg{biblatex-sbl} Package}
\author{David Purton\thanks{Email: \url{dcpurton@marshwiggle.net}}}
\date{2026-03-17 v2.0}

\maketitle

\begin{abstract}
  This package provides \pkg{biblatex} support for citations, bibliography and
  abbreviations in the format specified by the second edition of the
  \emph{Society of Biblical Literature (SBL) Handbook of Style} including
  updates on the \emph{SBL Handbook of Style} blog.
\end{abstract}

\tableofcontents

\section{Introduction}

\pkg{biblatex-sbl} provides support to \pkg{biblatex} and LaTeX for citations,
bibliography and abbreviations in the style recommended by the Society of
Biblical Literature (SBL). Shorthand citations and a list of abbreviations
containing journals, series, shorthands and ancient works are handled
automatically. Only note style citations, not author-date citations, are
supported. \pkg{biblatex-sbl} is compatible with \pkg{biblatex}'s support for
\pkg{hyperref}.

The style seeks to support the latest requirements outlined on the \emph{SBL
Handbook of Style} blog \autocite{sblhsblog}. All examples from the
handbook, student supplement, and blog are fully supported (noting that the
blog updates many recommendations).

There is also sophisticated handling of subsequent citations, reprints, and
the many unique entry types required by SBL style, such as lexicons,
dictionaries, and encyclopaedias.

\pkg{biblatex-sbl} is compatible with \pkg{biblatex}'s \pkg{hyperref} and
\pkg{babel} support, although custom strings are only provided for English at
this stage.

A companion bundle of packages and classes are distributed separately to
\pkg{biblatex-sbl}. These provide support for referencing Bible passages
(\pkg{bibleref-sbl}), font set up (\pkg{sblfonts}), indexing (\pkg{sblidx}),
term papers (\pkg{sblarticle}), theses (\pkg{sblreport}) and print ready books
(\pkg{sblbook}). You may also find the \pkg{scripture} package helpful in
formatting Bible quotations.

This manual only covers custom features of \pkg{biblatex-sbl}. For general
help with \pkg{biblatex} you should consult its extensive manual.

\subsection{Backward compatibility}

The blog has now made SBL style a rolling style that changes with each blog
post. Because of this, preserving backward compatibility between releases is
not feasible for time I have available to maintain this style and neither is
it possible to provide options to vary the style to cater for different
seminaries and theological colleges.

\textbf{In particular, version 2.0 and later of \pkg{biblatex-sbl} completely
breaks compatibility with the version 0.x releases.} If you need to access a
legacy release, you should download it from the GitHub repository and place
the style files locally in your project.\footnote{See
\url{https://github.com/dcpurton/biblatex-sbl/releases} for legacy (and new)
releases and \url{https://github.com/dcpurton/biblatex-sbl/tree/legacy} for
legacy source code.} Legacy 0.x versions are no longer maintained or
supported.

\subsection{Bug reports and feature requests}

Bug reports and feature requests can be made at the package GitHub repository.
See \url{https://github.com/dcpurton/biblatex-sbl}.

\section{Usage}

\subsection{Basic usage}

At a minimum, just load \pkg{biblatex} with |style=sbl|. By default many entry
types appear in the list of abbreviations rather than the bibliography so you
will almost certainly want to use both |\printbiblist{abbreviations}| and and
\cs{printbibliography}.

\begin{sblexample}[no output]
  \begin{verbatim}
  \documentclass{article}
  \usepackage[style=sbl]{biblatex}
  \addbibresource{<bibfile.bib>}
  \begin{dpcument}
  Filler text \autocite{<bibentry>}.
  \printbiblist{abbreviations}
  \printbibliography
  \end{document}
  \end{verbatim}
\end{sblexample}

\subsection{Bib entry set up}

Supported bib entries and fields are fully documented below. One of the best
ways to learn how to set up the bib entries for the style is to look through
the three example files which show every example from the handbook, the
student supplement and the blog. These files show the bib entries, the
citation commands and output including the list of abbreviations and
bibliography.
\begin{itemize}
  \item |biblatex-sbl-handbook-examples.pdf| shows all the examples from the
    handbook.
  \item |biblatex-sbl-studentsupplement-examples.pdf| shows all the examples
    from the student supplement to the handbook.
  \item |biblatex-sbl-blog-examples.pdf| shows all the examples from the blog.
\end{itemize}
These files should all be accessible with |texdoc|. Also in the documentation
directory is |biblatex-sbl.bib| which contains all bib entries used in the
example files.

The bib entry examples shown in example citations below are usually just
snippets showing a couple of relevant fields to the particular citation
command. You can then look up the full entry in |biblatex-sbl.bib|.

\subsection{Language and font set up}

Language and font set up can be done in the standard way for \pkg{biblatex}. I
recommend using \pkg{babel} and |lualatex|, especially for right-to-left
languages.

Note that \pkg{biblatex-sbl} contains many custom strings which are only
defined for English. Offers to develop and maintain translations for other
languages are welcome.

Set up for English, Greek and Hebrew using the SBL biblical fonts can be
simplified by using the \pkg{sblfonts} package. For example, the following
code sets up a document with Australian English as the main language and Greek
and Hebrew using the SBL fonts (provided they are installed). The following
example requires |lualatex|.

\begin{sblexample}
  \begin{verbatim}
  \documentclass[australian]{article}
  \usepackage[sblfonts]{sblfonts}
  \usepackage[style=sbl]{biblatex}
  \usepackage{csquotes}
  \addbibresource{biblatex-sbl.bib}
  \begin{document}
  Filler text \autocite[חֹזֶה II]{HALOT}.
  \end{document}
  \end{verbatim}

  \tcblower

  \setquotestyle{australian}
  \stdpunctuation

  Filler text.\footcite[חֹזֶה II]{HALOT}
\end{sblexample}

The big advantage of using |lualatex| with \pkg{babel} is that inline Greek
and Hebrew do not need to be marked up. They can just be written directly into
the document and bib entries.

\subsection{Citations}

In general, you should use \cs{autocite} and related commands for citations.
This will place citations in footnotes or within parentheses if already in a
footnote.

\subsubsection{Shorthands}

Many reference books, dictionaries, encyclopaedias and lexicons should be
cited by an abbreviation which should in turn appear in a list of
abbreviations. The abbreviation for a bib entry is set using the |shorthand|
field.

The font used for the abbreviation should match the format of the field to
which the abbreviation refers. So, for example, an abbreviation for the
authors of a book would be set in a Roman font, while the abbreviation for the
title of a book would be set in an italic font. By default \pkg{biblatex-sbl}
sets all abbreviations in an italic font, but this can be changed on a per-entry
basis by setting |shorthandformat=roman| in the entry options.

\begin{sblexample}
  \begin{verbatim}
  @reference{BDAG,
    options = {shorthandformat=roman},
    ...
  }
  @mvreference{HALOT,
    ...
  }
  \end{verbatim}

  \tcblower

  \examplecite[]{BDAG}

  \examplecite[]{HALOT}
\end{sblexample}

The separator between a work cited by abbreviation and the |postnote| is
dependent on what the |postnote| refers to. If the work is cited by page, then
the separator should be a comma. If the work is cited by section (§), then the
separator should be a space. This is handled by setting the |pagination| field
in the bib entry.

\begin{sblexample}
  \begin{verbatim}
  @collection{ANET,
    ...
  }
  @book{BDF,
    pagination = {section}
    ...
  }
  \end{verbatim}

  \tcblower

  \examplecite[][319]{ANET}

  \examplecite[][151]{BDF}
\end{sblexample}

\subsubsection{Multivolume works}

SBL has particular rules around the punctuation before and after the volume
number in a citation.
\begin{itemize}
  \item A multivolume work cited by abbreviation has a space before the
    volume.
  \item A multivolume work cited in full has a comma before the volume.
  \item A colon should separate the volume and page number(s).
  \item A period should separate the volume and other pagination styles (e.g.,
    paragraph or section).
\end{itemize}
\pkg{biblatex-sbl} uses the \pkg{biblatex} \cs{volcite} command and related
similar commands to cater to these requirements. You \emph{must} use
\cs{volcite} or similar when citing multivolume works otherwise punctuation
will be incorrect.

\begin{sblexample}
  \begin{verbatim}
  @mvcollection{ANF,
    volumes = {10},
    ...
  }
  @mvbook{ARAB,
    volumes = {2},
    pagination = {paragraph},
    ...
  }
  @mvcommentary{aune:1997-1998,
    volumes = {3},
    ...
  }
  \end{verbatim}

  \tcblower

  \examplevolcite[]{3}[63]{ANF}

  \examplevolcite[]{2}[407-416]{ARAB}

  \examplevolcite[]{1}[589]{aune:1997-1998}
\end{sblexample}

\subsubsection{Subsequent citations}

SBL style uses a full citation the first time a work is referenced, but then a
short form for subsequent citations (usually showing only the author and a
shortened title). If \pkg{hyperref} is loaded, the short title is usually
hyperlinked to the first citation.

\pkg{biblatex-sbl} automates the shortening of titles if possible while also
providing the |shorttitle| field to allow for a specific short title.

If no |shorttitle| is specified in the bib entry, then the short title is
constructed from the |title| field by:
\begin{itemize}
  \item Removing everything from the first colon as this is assumed to be the
    subtitle.
  \item Removing \emph{A}, \emph{An} or \emph{The} from the beginning.
\end{itemize}

A second feature of SBL style relates to citing chapters by different authors
in the same collection of works. In this case, the first citation of
subsequent chapters from the collection should use a short form of the
collection details. \pkg{biblatex-sbl} supports this using the \pkg{biblatex}
|crossref| field.

\begin{sblexample}
  \begin{verbatim}
  @collection{rogerson+lieu:2006,
    ...
  }
  @incollection{dell:2006,
    crossref = {rogerson+lieu:2006},
    ...
  }
  @incollection{davies:2006,
    crossref = {rogerson+lieu:2006},
    ...
  }
  \end{verbatim}

  \tcblower

  \examplecite[][415-416]{dell:2006}

  \examplecite[][99]{davies:2006}
\end{sblexample}

\subsubsection{Source divisions in ancient works}

Many ancient works are cited by a commonly agreed on source division (such as
book, chapter, section) instead of or as well as a page number in a particular
edition.

\pkg{biblatex-sbl} supports this with the aid of the
\pkg{biblatex-source-division} package.\footnote{Thanks to Maïeul Rouquette.
See \url{https://ctan.org/package/biblatex-source-division}.}

The syntax for specifying the source division is the same as for
\pkg{biblatex-source-division} so the source division is placed within
parentheses at the start of the |postnote| and is then optionally followed by
the location in the particular edition being cited. The text collection is
indicated using an |xref| field in the |ancienttext| bib entry.

\begin{sblexample}
  \begin{verbatim}
  @mvcollection{NPNF,
    ...
  }
  @ancienttext{augustine:letters,
    xref = {NPNF},
    ...
  }
  \end{verbatim}

  \tcblower

  \examplecite[][(28.3.5)252]{augustine:letters}
\end{sblexample}

\subsubsection{Translators of ancient works}

It is sometimes desirable to cite a particular translation of an ancient work.
For this purpose a set of variant citation commands are provided, e.g.,
\cs{atranscite}. The translator needs to be included in the bib entry of the
ancient work.

The format of the translator in the citation varies depending on whether the
source being cited is from within a text collection (indicated with the |xref|
field) or not.

\begin{sblexample}
  \begin{verbatim}
  @collection{ANET,
    ...
  }
  @ancienttext{legendsargon,
    translator = {Speiser, E. A.},
    xref = {ANET},
    ...
  }
  @{herodian:hist,
    translator = {Whittaker},
    ...
  }
  \end{verbatim}

  \tcblower

  \examplecite[trans]{legendsargon}

  \examplecite[trans][(2.2)]{herodian:hist}
\end{sblexample}

\subsubsection{Reprints}

\pkg{biblatex-sbl} supports three methods of citing reprints with varying
degrees of complexity.

If only the original publisher, location, and/or year are required, then use
the fields |origpublisher|, |origlocation|, and |origdate|.

\begin{sblexample}
  \begin{verbatim}
  @book{vanseters:1997,
    origpublisher = {Yale University Press},
    origdate = {1983},
    publisher = {eisenbrauns},
    date = {1997},
    ...
  }
  \end{verbatim}

  \tcblower

  \examplecite[][90]{vanseters:1997}
\end{sblexample}

When extra information is required, use a related entry with
|relatedtype = {reprint}|. A custom string can be specified instead of
``Repr.'' using the optional |relatedstring| field.  In this case no
punctuation is inserted after the |relatedstring|. You could think of the
default being |relatedstring = {\bibstring{reprint},}|.

\begin{sblexample}
  \begin{verbatim}
  @book{zerwick:2011,
    related = {zerwick:repr},
    relatedtype = {reprint}
    ...
  }
  @book{zerwick:repr,
    ...
  }
  \end{verbatim}

  \tcblower

  \examplecite[][360-362]{zerwick:2011}
\end{sblexample}

Finally, a full reprint history also uses the |related| field, but with some
other |relatedtype| apart from |relatedtype = {reprint}|.

\begin{sblexample}
  \begin{verbatim}
  @book{wellhausen:1883,
    ...
  }
  @book{wellhausen:1885,
    related = {wellhausen:1883},
    relatedtype = {translationof},
    ...
  }
  @book{wellhausen:1957,
    related = {wellhausen:1885},
    relatedtype = {reprintof},
    ...
  }
  \end{verbatim}

  \tcblower

  \examplecite[][20]{wellhausen:1957}
\end{sblexample}

\subsubsection{Other related works}

\pkg{biblatex-sbl} supports a number of more specialised ways of relating one
work to another.

Some journal articles are published across multiple volumes, but can be cited
as one article. This kind of citation uses |relatedtype = {multivolarticle}|
and should be cited with \cs{avolcite} or similar. Note that there is no
|@mvarticle| bib entry type, as this type of reference is very rare. Just use
|@article|.

\begin{sblexample}[lefthand ratio=0.55]
  \begin{verbatim}
  @article{wellhausen:1876-1887,
    related = {wellhausen:1876, wellhausen:1877},
    relatedtype = {multivolarticle},
    ...
  }
  @article{wellhause:1876,
    volume = {21},
    ...
  }
  @article{wellhause:1877,
    volume = {22},
    ...
  }
  \end{verbatim}

  \tcblower

  \examplevolcite[]{21}[434]{wellhausen:1876-1877}
\end{sblexample}

A particularly niche situation arose on the SBL blog at
\url{https://sblhs2.com/2018/01/18/citing-text-collections-10-lcl/} where a
question was asked concerning citing from a LCL volume containing works by
multiple authors each with a separate translator. When citing from a work
by an author other than the first author listed in the volume's title, SBL
suggested using a cross reference in the bibliography to point to the main
bibliography entry. \pkg{biblatex-sbl} supports this using a combination of
|relatedtype = {see}| and an |execute| field. It's not pretty, but it does
work.

There's a lot of bib entries that go into making this, so rather than list
them here, you can look up |aristotle:poetics:book| and following entries in
|biblatex-sbl.bib|. To make things more complicated the main bibliography
entry uses the |related| field to append the other two works to the first
title.

Several more compiles and runs of |biber| are required than you wish for,
unless you add a couple of entries to \cs{nocite}.

\begin{sblexample}[no code]
  \nocite{aristotle:poetics:book, aristotle:poetics:book:short}
  \examplecite[]{longinus:sublime}

  \examplebibliography
\end{sblexample}

A final supported type of relating one work to another deals with citing a
quotation from within another work. Note that SBL discourages this as the
primary source should be consulted. This type of citation uses the |xref| and
|xrefstring| fields.

\begin{sblexample}
  \begin{verbatim}
  @book{edwards:1999,
    ...
  }
  @ancienttext{victorinus:ephesians,
    xref = {edwards:1999},
    xrefstring = {quoted in},
    ...
  }
  \end{verbatim}

  \tcblower

  \nocite{ACCS}
  \examplecite[][(1.2.12)129]{victorinus:ephesians}
\end{sblexample}

\subsubsection{Reference works}

Dictionaries, encyclopaedia and lexica deserve a special mention.
\pkg{biblatex-sbl} uses the |@mvreference|, |@reference| and |@inreference|
entry types to support these. |@inreference| is used to cite signed articles
which should appear in the bibliography. Unsigned entries use the
|@mvreference| or |@reference| entry directly. Typically reference works with
unsigned entries in them use |pagination = {subverbo}| and the articles are
referenced by word under consideration rather than page number. Unsigned
articles do not appear in the bibliography. The reference work itself will
appear in the list of abbreviation if cited by its abbreviation or in the
bibliography otherwise.

\begin{sblexample}
  \begin{verbatim}
  @mvreference{EDNT,
    pagination = {subverbo},
    ...
  }
  @inreference{lattke:kakia,
    xref = {EDNT},
    ...
  }
  \end{verbatim}

  \tcblower

  \examplecite[][Ἅγαβος]{EDNT}

  \examplecite[]{lattke:kakia}
\end{sblexample}

\subsection{Bibliography}

The bibliography is printed using the standard \pkg{biblatex} command,
\cs{printbibliography}. Some bib entries are excluded from the bibliography by
default in order to comply with SBL recommendations (e.g., references cited by
abbreviation, most ancient sources, blogs, etc.). Often these defaults can be
overridden by including |options = {skipbib=false}| in the bib entry.

\subsection{List of abbreviations}

SBL style makes extensive use of abbreviations, so it is almost always
necessary to include a list of abbreviations with
|\printbiblist{abbreviations}|. If \pkg{hyperref} is loaded then abbreviations
will hyperlink to the list of abbreviations.

Many longer works split the list of abbreviations into three sections: a list
of abbreviations relating to ancient sources, a list of abbreviations relating
to secondary sources, and a list of sigla and other abbreviations.

\subsubsection{Ancient sources}

A list of abbreviations of ancient sources can be printed by passing
|type=ancienttext| to \cs{printbiblist}. Preferred abbreviations for ancient
sources are specified in the handbook and on the blog. SBL now prefers to use
Latin abbreviations over English ones.

To appear in the list of abbreviations and |@ancienttext| must have a
|shorttitle|. If two works have the same short title, then SBL specifies that
the works should be separated with a semi-colon in the list of abbreviations.
This happens automatically.

\begin{sblexample}[lefthand ratio=0.35]
  \begin{verbatim}
  @ancienttext{1QM,
    title = {War Scroll},
    shorttitle = {1QM}
  }
  @ancienttext{cicero:agr,
    shorttitle = {Agr.},
    ...
  }
  @ancienttext{philo:agr,
    shorttitle = {Agr.},
    ...
  }
  @ancienttext{plutarch:ant,
    shorttitle = {Ant.},
    ...
  }
  \end{verbatim}

  \tcblower

  \begin{verbtext}
      \printbiblist
        [heading=subbibliography,
         title=Ancient Sources,
         type=ancienttext]
        {abbreviations}
  \end{verbtext}

  \nocite{1QM, cicero:agr, philo:agr, plutarch:ant}

  \vspace{-\baselineskip}

  \subsubsection*{Ancient Sources}

  \printbiblist [heading=none, title=Ancient Sources,
    type=ancienttext]{abbreviations}
\end{sblexample}

\subsubsection{Secondary sources}

Secondary sources will be included in a list of abbreviations for bib entries
containing any one of the fields |shorthand|, |shortseries| and/or
|shortjournal|.

\begin{sblexample}[lefthand ratio=0.35]
  \begin{verbatim}
  @reference{BDB,
    shorthand = {BDB},
    ...
  }
  @article{miller:1984,
    shortjournal = {JSOT},
    ...
  }
  @book{salters:2010,
    shortseries = {ICC},
    ...
  }
  \end{verbatim}

  \tcblower

  \begin{verbtext}
      \printbiblist
        [heading=subbibliography,
         title=Secondary Sources,
         nottype=ancienttext,
         nottype=abbreviation]
        {abbreviations}
  \end{verbtext}

  \nocite{BDB, miller:1984, salters:2010}

  \vspace{-\baselineskip}

  \subsubsection*{Secondary Sources}

  \printbiblist [heading=none, title=Ancient Sources,
    nottype=ancienttext, nottype=abbreviation]{abbreviations}
\end{sblexample}

\subsubsection{Sigla and grammatical abbreviations}

\pkg{biblatex-sbl} includes \emph{very} basic support for general
abbreviations, sigla and acronyms. These are supported by a basic
|@abbreviation| bib entry type with a |shorthand| and corresponding
|definition| field. Abbreviations can then be included in the text and added
to the list of abbreviations using the \cs{abbrev} command. 

\begin{sblexample}[lefthand ratio=0.35]
  \begin{verbatim}
  @reference{>,
    shorthand = {>},
    definition = {omits the lemma}
  }
  @article{abl,
    shorthand = {abl.},
    definition = {ablative}
  }
  \end{verbatim}

  \tcblower

  \begin{verbtext}
      \printbiblist
        [heading=subbibliography,
         title=Sigla and Grammatical Abbreviations,
         type=abbreviation]
        {abbreviations}
  \end{verbtext}

  \nocite{>, abl}

  \vspace{-\baselineskip}

  \subsubsection*{Sigla and Grammatical Abbreviations}

  \printbiblist [heading=none, title=Ancient Sources,
    type=abbreviation]{abbreviations}
\end{sblexample}

\subsection{Index of modern authors}

Passing the option |indexing=cite| to \pkg{biblatex-sbl} activates indexing of
modern authors. (SBL tends not to index names in the bibliography and list of
abbreviations, neither does it include titles in the index as \pkg{biblatex}
does by default.)

Set up for indexing of modern authors (along with subjects and ancient
sources) according to SBL style can be simplified by using the \pkg{sblidx}
package.

\pkg{biblatex-sbl} does not include |@ancienttext| entry types in the index as
these are often index in a similar way to Bible references and the set up will
likely be unique to a particular project. \pkg{bibleref-sbl} could be useful
here.

\section{Package reference}

Many (but by no means all) of the standard \pkg{biblatex} options, commands,
entry types, fields and localisation strings are supported by
\pkg{biblatex-sbl}.

The following section documents things which are unique to \pkg{biblatex-sbl}
or which behave in unique ways.

\subsection{Options}

\pkg{biblatex-sbl} loads the \pkg{biblatex} |verbose-ibid| style and then
executes the following options by default:
\begin{quote}
  \ttfamily\raggedright
  citepages=omit, citetracker=context, dateabbrev=false, ibidtracker=false,
  idemtracker=citation, language=american, maxbibnames=99, mincrossrefs=2,
  minxrefs=1, nametracker=context, pagetracker=true, sorting=nwty,
  uniquework=true
\end{quote}
The following options are unique to \pkg{biblatex-sbl} or behave in a unique
way.

\subsubsection{Load-time options}

\begin{function}{citepages}
  \begin{syntax}
    = omit \textbar\ separate\hfill Default: omit
  \end{syntax}
  By default SBL recommends that full pages for a chapter or article be
  included in the bibliography and only the page or pages under consideration
  be referenced in the first citation.
\end{function}

If there is no bibliography, then setting |citepages=separate| includes the
full page range in the first citation. The page under consideration is then
included after the string |thiscite|, which is defined as `here' by default.

One exception to this is in the first citation to a multi-part journal article
spread of two volumes. In this case, the behaviour always matches that of
|citepages=separate|.

\subsubsection{Entry options}

\begin{function}{nonlatinbooktitleformat, nonlatinmaintitleformat, nonlatintitleformat}
  \begin{syntax}
    = \meta{boolean}\hfill Default: false
  \end{syntax}
  These entry options controls how a title in a non-Latin alphabet is
  formatted, if you wish to cite by this title rather than a translated title.
  The translated title is then placed in |translatedtitle|,
  |translatedbooktitle| or |translatedmaintitle|.
\end{function}

In such cases, the non-Latin title should be formatted in a plain Roman font,
rather than italic or quoted Roman font. However, you need to tell
\pkg{biblatex-sbl} that your bib entry is using a non-Latin script for the
title. This can by done using |options = {nonlatintitle}| in the bib entry.

\begin{function}{shorthandformat}
  \begin{syntax}
    = italic \textbar roman\hfill Default: italic
  \end{syntax}
  The format of a |shorthand| field in SBL style needs to match what the
  abbreviation points to. So if the |shorthand| refers to the title of the
  work, it should be printed in italics, whereas if the |shorthand| refers to
  the authors of the work it it should be set in a Roman font. By default the
  |shorthand| is set using italics, but this can be changed for a bib entry
  using |options = {shorthandformat=roman}|.
\end{function}

\begin{function}{usetitle}
  \begin{syntax}
    = true \textbar\ false\hfill Default: true
  \end{syntax}
  For bib entry types that can have a |maintitle| in addition to a |title|
  (|@book|, |@collection|, |@commentary|, |@reference|) SBL usually places the
  |title| first and then locates this in the |maintitle|. However, there are
  some situations where it makes more sense to reference the work by its
  |maintitle| because the |title| is overly generic (e.g., \emph{Books 1–3}).
  In these cases, set use |options = {usetitle=false}| to place the |title|
  after the |maintitle|.
\end{function}

\begin{function}{usexref}
  \begin{syntax}
    = true \textbar\ false\hfill Default: true
  \end{syntax}
  Generally, ancient works which are part of a text collection include the
  text collection in the citation. One exception to this is SBL's treatment of
  ancient epistles and homilies,\footnote{See §6.4.4 of the handbook.} where
  the collection does not appear in the citation, but it still needs to appear
  in the bibliography. This behaviour can be achieved by placing the text
  collection in the |xref| field as usual and then using
  |options = {usexref=false}|.
\end{function}

\subsection{Commands}

\subsubsection{Citation commands}

\paragraph{Main citation commands}

\begin{function}{\autocite, \autocite*, \Autocite, \Autocite*}
  \begin{syntax}
    \oarg{prenote}[(\meta{source division})\meta{postnote}]\marg{key}
  \end{syntax}
  \cs{autocite} inserts a citation as a footnote. If used in a footnote, the
  citation is placed in parentheses. The starred variant suppresses the
  author, editor, or translator (provided the entry options are set to use
  them). It works as in the standard \pkg{biblatex} styles, except that that
  \meta{postnote} argument can be divided into two using parentheses to
  specify a source division for ancient works.
\end{function}

\cs{Autocite} is similar to \cs{autocite} but capitalises the name prefix of
the first name in the citation if provided that there is a name prefix.
This only makes a difference if the |autocite| option has been set to |plain|
or |inline|.

As with the \pkg{biblatex} package, the behaviour of \cs{autocite} can be
changed with the |autocite| load-time option.

\begin{function}{\cite, \cite*, \Cite, \Cite*}
  \begin{syntax}
    \oarg{prenote}[(\meta{source division})\meta{postnote}]\marg{key}
  \end{syntax}
  \cs{cite} works in the same way as \cs{autocite} except that the citation is
  placed directly into the text instead of in a footnote. The starred variant
  suppresses the author, editor, or translator (provided the entry options are
  set to use them).
\end{function}

\cs{Cite} is similar to \cs{cite} but capitalises the name prefix of the first
name in the citation if provided that there is a name prefix.

\begin{function}{\parencite, \parencite*, \Parencite, \Parencite*}
  \begin{syntax}
    \oarg{prenote}[(\meta{source division})\meta{postnote}]\marg{key}
  \end{syntax}
  \cs{parencite} works in the same way as \cs{autocite} except that the
  citation is placed inside parentheses instead of in a footnote. The starred
  variant suppresses the author, editor, or translator (provided the entry
  options are set to use them). This is most useful for citing primary
  sources.
\end{function}

\cs{Parencite} is similar to \cs{parencite} but capitalises the name prefix of
the first name in the citation if provided that there is a name prefix.

\paragraph{Volume citation commands}

Multi-volume references \emph{must} be cited using this family of citation
commands to ensure correct delimiters before and after the volume number in
the citation.

\begin{function}{\avolcite, \avolcite*, \Avolcite, \Avolcite*}
  \begin{syntax}
    \oarg{prenote}\marg{volume}[(\meta{source division})\meta{postnote}]\marg{key}
  \end{syntax}
  This function is analogous to \cs{autocite}, but allows specifying the
  \meta{volume} when citing a multi-volume work.
\end{function}

\begin{function}{\pvolcite, \pvolcite*, \Pvolcite, \Pvolcite*}
  \begin{syntax}
    \oarg{prenote}\marg{volume}[(\meta{source division})\meta{postnote}]\marg{key}
  \end{syntax}
  This function is analogous to \cs{parencite}, but allows specifying the
  \meta{volume} when citing a multi-volume work.
\end{function}

\begin{function}{\volcite, \volcite*, \Volcite, \Volcite*}
  \begin{syntax}
    \oarg{prenote}\marg{volume}[(\meta{source division})\meta{postnote}]\marg{key}
  \end{syntax}
  This function is analogous to \cs{cite}, but allows specifying the
  \meta{volume} when citing a multi-volume work.
\end{function}

\paragraph{Translator citation commands}

When citing a translation of an ancient work, the translator of the work needs
to be included. The following commands do this providing the translator is
specified in the |translator| field (or inherited via the |crossref| field).

These functions only make sense for |@ancienttext| entry types.

\begin{function}{\atranscite, \atranscite*, \Atranscite, \Atranscite*}
  \begin{syntax}
    \oarg{prenote}[(\meta{source division})\meta{postnote}]\marg{key}
  \end{syntax}
  This function is analogous to \cs{autocite}, but includes the translator.
\end{function}

\begin{function}{\ptranscite, \ptranscite*, \Ptranscite, \Ptranscite*}
  \begin{syntax}
    \oarg{prenote}[(\meta{source division})\meta{postnote}]\marg{key}
  \end{syntax}
  This function is analogous to \cs{parencite}, but includes the translator.
\end{function}

\begin{function}{\transcite, \transcite*, \Transcite, \Transcite*}
  \begin{syntax}
    \oarg{prenote}[(\meta{source division})\meta{postnote}]\marg{key}
  \end{syntax}
  This function is analogous to \cs{cite}, but includes the translator.
\end{function}

\begin{function}{\avoltranscite, \avoltranscite*, \Avoltranscite, \Avoltranscite*}
  \begin{syntax}
    \oarg{prenote}\marg{volume}[(\meta{source division})\meta{postnote}]\marg{key}
  \end{syntax}
  This function is analogous to \cs{avolcite}, but includes the translator.
\end{function}

\begin{function}{\pvoltranscite, \pvoltranscite*, \Pvoltranscite, \Pvoltranscite*}
  \begin{syntax}
    \oarg{prenote}\marg{volume}[(\meta{source division})\meta{postnote}]\marg{key}
  \end{syntax}
  This function is analogous to \cs{pvolcite}, but includes the translator.
\end{function}

\begin{function}{\voltranscite, \voltranscite*, \Voltranscite, \Voltranscite*}
  \begin{syntax}
    \oarg{prenote}\marg{volume}[(\meta{source division})\meta{postnote}]\marg{key}
  \end{syntax}
  This function is analogous to \cs{volcite}, but includes the translator.
\end{function}

\paragraph{Multicite citation commands}

Each of the above commands also has multicite variants (\cs{autocites},
\cs{parencites}, \cs{cites}, etc.). See the main \pkg{biblatex} package
documentation for syntax and usage.

Each citation \meta{postnote} can by split to include a \meta{source division}
as above.

\paragraph{Specialised citation commands}

The following specialised citation commands are also available.

% \citeauthor, \citefullauthor, \citeshortauthor (plus starred, plus capitals)

% \citetitle, \citetitle*

% \citecollection, \parencitecollection, \transcitecollection, \ptranscollection

% \fullcite (plus variants)

\subsubsection{Bibliography and list of abbreviations}

% \printbibliography

% \printbiblist{abbreviations}

\subsubsection{Miscellaneous commands}

% \abbrev

% \colno, \colsno

% \lno, \llno, \lineno, \linesno

% \nopnfmt

% \sno, \ssno

% \sv, \svv

\subsection{Entry types}

\subsection{Entry fields}

\subsection{Localisation strings}


\end{document}
